---
title: "Data Medical GIS"
author: "Taejoo Chae"
date: "2019년 3월 9일"
output: html_document
---

# MEDICAL SUPPLIERS IN USA

This code provides simple Geographic Information System(GIS) coded by R. 

Data is downloaded from a federal government website managed by the U.S. Department of Health & Human Services
200 Independence Avenue, S.W. - Washington, D.C. 20201, or HealthData.gov. The website's address is   <https://healthdata.gov/dataset/supplier-directory-data>.

Data is released in 2019-03-08. If updated data is necessary, please use above website address.


## Data & package preparation.

After data is downloaded, it is loaded using Rstudio program along with several packages.

Please change the ROOT.DIR's directory information.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

ROOT.DIR = "e:/ITMS2018/R/datamedical/"

train = read.csv(file.path(ROOT.DIR, "Supplier_Directory_Data.csv"))
train$Competitive.Bid.Service.Area.Name = NULL
train[,1] = NULL
head(train)


library(ggmap)
library(fiftystater)
library(raster)
library(rgeos)
library(maptools)
library(rgdal)

```

## Data inspection

It is not important here, but I wanted to check if there are any NA(Not Applicable) values and unique values in this data. 

Using na_val as NA locater, Zip.Plus.4 and Toll.Free.Telephone categories are having NAs. 

Using unq_val as unique value finder, there are 56 states and 7344 cities in USA. Probably will use city information later, but this time, only state information will be used.

```{r cars}

category1 = data.frame(table(train$Product.Category.Name))
category1 = category1[order(category1$Freq, decreasing = TRUE), ]


str(train)

na_val = sapply(train, function(x) sum(is.na(x)))
#this is using function x which is sum(is.na(x))

# count unique records per variable
unq_val <- sapply(train, function(x) length(unique(x)))

splittrain1 = split(train, train$State)
#splittrain["AK"]

splittrain2 = split(train, train$Product.Category.Name)

```

## Ranking by state

From train data, number and rate of medical supplier by each state information are gathered. 

```{r}
maxmin = table(train$State)
maxmin = data.frame(maxmin)

ordermaxmin = maxmin[order(maxmin$Freq, decreasing = TRUE), ]
ordermaxmin$rate = ordermaxmin$Freq/sum(ordermaxmin[,2])*100

#write.csv(ordermaxmin, file = "stateinfo.csv", row.names=FALSE)

```

California has 49631 medical supliers, or medical stores, which is number 1 in USA. After CA, Texas and New York's number of medical stores are in 2nd and 3rd ranking.

This data is exported as an csv file and edited.
Please refer stateinfo.csv for further details.


## Visualize data

By using stateinfo.csv, frequency data is visualized.

Rate and full name of each state is used.

```{r pressure, echo=FALSE}
ordermaxmin2 = read.csv(file.path(ROOT.DIR, "stateinfo.csv"))

data("fifty_states")
p1 = ggplot(ordermaxmin2, aes(map_id = state)) + 
  
  # map points to the fifty_states shape data
  geom_map(aes(fill = rate), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "") +
  theme(legend.position = "bottom", 
        panel.background = element_blank())

# add border boxes to AK/HI
p1 + fifty_states_inset_boxes() 

```
